\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{#2 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\linewidth}{@{\extracolsep{\fill}}l r}
      \textbf{#1} & \textit{\small #4} \\
      \textit{\small #2} & \textit{\small #3} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Sebastián Ignacio Urbina Gajardo}} & 
  Email: \href{mailto:sebastian.urbina97@gmail.com}{sebastian.urbina97@gmail.com} \\
  \href{https://www.linkedin.com/in/sebaurbina/}{LinkedIn} |
  \href{https://github.com/SebasUrbina}{GitHub} |
  \href{https://sebasurbina.github.io/}{Website} & 
  Mobile: +(56)-966719190 \\
\end{tabular*}

\vspace{8pt}
\noindent
Software Engineer with experience building production-grade backend and AI systems. Specialized in developing scalable agentic services, distributed processing pipelines, and cloud-native infrastructure. Strong foundation in programming, systems design, and cross-functional technical leadership. Focused on delivering reliable, high-performance systems with measurable impact.

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {MSc in Data Science; GPA: 6.7/7.0}{2023 - 2024}
    \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {BSc in Industrial Engineering; GPA: 6.4/7.0}{2018 - 2024}
      \resumeSubHeadingListStart
        \resumeSubItem{Best Graduate of the Year 2024: }{ 1/244}
        \resumeSubItem{Outstanding student: }{2018, 2019, 2020, 2021 \& 2022.}
        \resumeSubItem{Teaching Assistant: }{Data Analysis and Causal Inference, Introduction to Deep Learning, Finance II \& Seminar of Thinking.}
      \resumeSubHeadingListEnd
  \resumeSubHeadingListEnd

\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{}{\textbf{Languages:} Python, JavaScript, TypeScript, SQL, R, Go (learning).}
   \resumeSubItem{}{\textbf{Technologies:} AWS, GCP, Kubernetes, Docker, Kafka, Git, FastAPI, LangChain, LangGraph, OpenAI SDK, Prometheus, Grafana.}
 \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bci Bank}{Santiago, Chile}
      {Machine Learning Engineer}{Aug 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Scalable Agentic Services: }
          {Designed and deployed containerized agent services on Kubernetes, supporting 100 recurring users and 500 account executives across internal channels including Google Chat and web interfaces.}
        \resumeItem{Performance Optimization: }
          {Reduced end-to-end response latency from 30s to 10s through architectural improvements, async pipelines, and optimized LLM tool use.}
        \resumeItem{Distributed Callbacks Architecture: }
          {Implemented Kafka-based callback handling for LangGraph agents; built consumer pipeline that delivered events from Kafka to Databricks for downstream processing and analytics.}
        \resumeItem{API and System Design: }
          {Built REST services powering internal Generative AI products; implemented rate limiting (100/s), pagination for conversational agents, and monitoring integrations.}
        \resumeItem{Production Reliability: }
          {Built structured logging, Prometheus metrics, and alerting dashboards in Grafana; deployed HPA (up to 3 replicas) to ensure stability under burst demand.}
      \resumeItemListEnd

    \resumeSubheading
      {Entel}{Santiago, Chile}
      {AI Engineer}{Apr 2025 -- Aug 2025}
      \resumeItemListStart
        \resumeItem{Backend + AI Infra Ownership: }
          {Led design and deployment of modular AI microservices with CI/CD pipelines across dev/staging/prod, ensuring reliability and rapid iteration.}
        \resumeItem{Cost Reduction: }
          {Achieved 60× cost reduction in transcription workloads by replacing external processors with a scalable AWS container-based service.}
        \resumeItem{Stakeholder Communication: }
          {Delivered technical roadmaps and architectural proposals to engineering managers, directors, and executive leadership.}
      \resumeItemListEnd

    \resumeSubheading
      {Entel}{Santiago, Chile}
      {Data Scientist Specialist}{Apr 2024 -- Mar 2025}
      \resumeItemListStart
        \resumeItem{LLM-Powered Systems: }
          {Built internal RAG chatbot on AWS using ECS, Lambda, and RDS, enabling employees to query technical documentation with high retrieval accuracy.}
        \resumeItem{MVP Development: }
          {Developed POCs and MVPs to validate Generative AI use cases; provided data insights to inform product decisions.}
        \resumeItem{Cloud Infrastructure: }
          {Managed AWS deployments, cost monitoring, and service provisioning for internal AI initiatives.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}
